\input{latex-korrekturansicht-vorspann}

               \section[Arthur Schnitzler an Hermann Bahr, 20. 8. 1903]{ Arthur Schnitzler an Hermann Bahr, 20. 8. 1903}\nopagebreak\mylabel{v}\rehead{ }\normalsize\beginnumbering\briefempfaengerindex{Bahr, Hermann@\textsc{Bahr, Hermann}!zzzSchnitzler, Arthur@\emph{von Arthur Schnitzler}!1903-08-201@{20. 8. 1903}|(be} \toendnotes[C]{\smallbreak\pagebreak[2]} \Standort{TMW, HS AM 60164 Ba.}
\physDesc{Bildpostkarte
\newline{}Handschrift: Bleistift, deutsche Kurrent\newline{}Versand: Stempel: »\nobreak{}\oindex{Lavarone@\textbf{Lavarone}, \emph{Besiedelter Ort (A.BSO)}|pwk}Lavarone, 21{[}. 8. 1903{]}\nobreak{}«.  }\buchAbdrucke{\weitereDrucke{1) \emph{20. 8. 1903, Abschrift.} In: Arthur Schnitzler: \emph{The Letters of Arthur Schnitzler to Hermann Bahr}. Edited, annotated, and with an introduction, by Donald G.
                        Daviau. Chapel Hill: \emph{The University of North Carolina Press} 1978, S. 79 (University of North Carolina studies in the Germanic languages
                        and literatures, 89).} \weitereDrucke{2) Hermann Bahr, Arthur Schnitzler: \emph{Briefwechsel, Aufzeichnungen, Dokumente (1891–1931)}. Hg. Kurt Ifkovits und Martin Anton Müller. Göttingen: \emph{Wallstein} 2018, S. 270.} }\pstart{}{\pb}Herrn Hermann Bahr\pend{}\pstart{}\textcolor{pink}{Wien-Ob St Veit}{}\ledrightnote{\textcolor{pink}{Ober Sankt Veit}}\pend{}\pstart{}\textcolor{pink}{Veitliſſengaſſe}{}\ledrightnote{\textcolor{pink}{Veitlissengasse}}\pend{}{\bigskip}\pstart
           \noindent{}\centering{}\textcolor{gray}{\textbf{{\pb}\textcolor{pink}{Grand Hôtel, Lavarone}{}\ledrightnote{\textcolor{pink}{Lavarone}}, 1200 Meter
                  über dem Meer}}\pend
           \pstart
           {\pb}20. 8. 903.\pend
           \pstart
           Herzlichen Gruſs \spacefill\mbox{Arthur}\pend
           \endnumbering\briefempfaengerindex{Bahr, Hermann@\textsc{Bahr, Hermann}!zzzSchnitzler, Arthur@\emph{von Arthur Schnitzler}!1903-08-201@{20. 8. 1903}|)be}\mylabel{h}  \input{latex-korrekturansicht-abspann}
      